Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-17 longSC.tex
with hydro only

where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_SC_bestfits.eps}}\hspace{-0.60cm}
                        \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_vn_bestfits.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for all SC observables (a) and individual harmonics $v_n$ (b). The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}

The results for the SC observables are presented in Fig~\ref{fig:Figure_A5}(a) and the ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}(b). We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08), the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by the model compared to the event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_A5}(b), showing that the ${\chi}^2$ values for $v_n$ are much larger for the VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the models. As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$. This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.

>>>>

where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
%The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad_wo_ampt.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
        %The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}

%The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively. The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for the VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
%The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values are worst for $v_n$ among the models.
%The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations. As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$. This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively. The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08), the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by the model compared to the event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger for VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations. As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$. This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
